HBCC - DLPFC - FEATURECOUNTS - GRCh38 - CQN - Sparse Model

### 2019-12-17 cmc-rnaseq-de/HBCC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
fix dropped gene ids in rownames
explicit specification of mart host

# Limit HBCC DLPFC Counts
COUNT <- COUNT[,colnames(COUNT) %in% METADATA$SampleID]

@@

# Define biomart object
mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", host = "ensembl.org", dataset = "hsapiens_gene_ensembl")

>>>>

# Limit HBCC DLPFC Counts
rownames(COUNT) = COUNT$Geneid
COUNT <- COUNT[,colnames(COUNT) %in% METADATA$SampleID]

@@

# Define biomart object
mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", host = "oct2018.archive.ensembl.org", dataset = "hsapiens_gene_ensembl")
